Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-25 survey/survey.tex
some progress in section 4. Moved some things around to make more sense for the reader, and then wrote a bit more.

@@

\begin{figure}[t]
Let $c, c_1, c_2, c_3 : t_1 \leftrightarrow t_2$ and $c', c'' : t_3 \leftrightarrow t_4$:
\[\def\arraystretch{1.3}
\begin{array}{c}
  {\idc \odot \, c \Leftrightarrow c}
\quad
  {c \, \odot \idc \, \Leftrightarrow c}
\quad
  {c\,\, \odot\,!\, c \Leftrightarrow \idc}
\quad
  {!\, c \odot c \Leftrightarrow \idc}
\\
  {c \Leftrightarrow c}
\quad
\Rule{}
  {c_1 \Leftrightarrow c_2 \quad c_2 \Leftrightarrow c_3}
  {c_1 \Leftrightarrow c_3}
  {}
\quad
\Rule{}
  {c_1 \Leftrightarrow c' \quad c_2 \Leftrightarrow c''}
  {c_1 \odot c_2 \Leftrightarrow c' \odot c''}
  {}
\end{array}\]
\caption{\label{figh}Signatures of level-2 $\Pi$-combinators: identity and composition}
\end{figure}

@@

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

\begin{figure}[t]
Let $c_1 : t_1 \leftrightarrow t_2$, $c_2 : t_3 \leftrightarrow t_4$, $c_3 : t_1 \leftrightarrow t_2$, and $c_4 : t_3 \leftrightarrow t_4$. \\
Let $a_1 : t_5 \leftrightarrow t_1$,  $a_2 : t_6 \leftrightarrow t_2$, $a_3 : t_1 \leftrightarrow t_3$, and $a_4 : t_2 \leftrightarrow t_4$.
\[\def\arraystretch{1.3}
\begin{array}{c}
\Rule{}
  {c_1 \Leftrightarrow c_3 \quad c_2 \Leftrightarrow c_4}
  {c_1 \oplus c_2 \Leftrightarrow c_3 \oplus c_4}
  {}
\qquad
\Rule{}
  {c_1 \Leftrightarrow c_3 \quad c_2 \Leftrightarrow c_4}
  {c_1 \otimes c_2 \Leftrightarrow c_3 \otimes c_4}
  {}
\\
  {\idc \oplus \, \idc \, \Leftrightarrow \idc}
\qquad
  {\idc \otimes \, \idc \, \Leftrightarrow \idc}
\\
  {(a_1 \odot a_3) \oplus (a_2 \odot a_4) \Leftrightarrow (a_1 \oplus a_2) \odot (a_3 \oplus a_4)}
\\
  {(a_1 \odot a_3) \otimes (a_2 \odot a_4) \Leftrightarrow (a_1 \otimes a_2) \odot (a_3 \otimes a_4)}
\end{array}\]
\caption{\label{fige}Signatures of level-2 $\Pi$-combinators: functors}
\end{figure}

The constructs in Fig.~\ref{fige} \ldots
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

@@

The constructs in Fig.~\ref{figd} \ldots
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

@@

The constructs in Fig.~\ref{figc} \ldots
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

>>>>

\begin{figure}[t]
Let $c_1 : t_1 \leftrightarrow t_2$, $c_2 : t_3 \leftrightarrow t_4$, $c_3 : t_1 \leftrightarrow t_2$, and $c_4 : t_3 \leftrightarrow t_4$. \\
Let $a_1 : t_5 \leftrightarrow t_1$,  $a_2 : t_6 \leftrightarrow t_2$, $a_3 : t_1 \leftrightarrow t_3$, and $a_4 : t_2 \leftrightarrow t_4$.
\[\def\arraystretch{1.3}
\begin{array}{c}
\Rule{}
  {c_1 \Leftrightarrow c_3 \quad c_2 \Leftrightarrow c_4}
  {c_1 \oplus c_2 \Leftrightarrow c_3 \oplus c_4}
  {}
\qquad
\Rule{}
  {c_1 \Leftrightarrow c_3 \quad c_2 \Leftrightarrow c_4}
  {c_1 \otimes c_2 \Leftrightarrow c_3 \otimes c_4}
  {}
\\
  {(a_1 \odot a_3) \oplus (a_2 \odot a_4) \Leftrightarrow (a_1 \oplus a_2) \odot (a_3 \oplus a_4)}
\\
  {(a_1 \odot a_3) \otimes (a_2 \odot a_4) \Leftrightarrow (a_1 \otimes a_2) \odot (a_3 \otimes a_4)}
\end{array}\]
\caption{\label{fige}Signatures of level-2 $\Pi$-combinators: functors}
\end{figure}

Starting with the simplest constructions, the first two constructs in
Fig.~\ref{fige} are the level-2 analogs of $+$ and $*$, which respectively
model combinator-level choice composition and parallel composition (of
equivalences).  These allow us to ``build up'' larger equivalences from smaller
ones.  The next two express that both of these composition operators distribute
over sequential composition $\odot$ (and vice versa).

@@

\begin{figure}[t]
Let $c, c_1, c_2, c_3 : t_1 \leftrightarrow t_2$ and $c', c'' : t_3 \leftrightarrow t_4$:
\[\def\arraystretch{1.3}
\begin{array}{c}
  {\idc \odot \, c \Leftrightarrow c}
\quad
  {c \, \odot \idc \, \Leftrightarrow c}
\quad
  {c\,\, \odot\,!\, c \Leftrightarrow \idc}
\quad
  {!\, c \odot c \Leftrightarrow \idc}
\\
  {\idc \oplus \, \idc \, \Leftrightarrow \idc}
\qquad
  {\idc \otimes \, \idc \, \Leftrightarrow \idc}
\\
  {c \Leftrightarrow c}
\quad
\Rule{}
  {c_1 \Leftrightarrow c_2 \quad c_2 \Leftrightarrow c_3}
  {c_1 \Leftrightarrow c_3}
  {}
\quad
\Rule{}
  {c_1 \Leftrightarrow c' \quad c_2 \Leftrightarrow c''}
  {c_1 \odot c_2 \Leftrightarrow c' \odot c''}
  {}
\end{array}\]
\caption{\label{figh}Signatures of level-2 $\Pi$-combinators: identity and composition}
\end{figure}

@@

@@

The constructs in Fig.~\ref{figd} express how unit elimination ``in the middle''
can be expressed either as operating on the right or, (after re-association) on the left.

@@

The constructs in Fig.~\ref{figc} are significantly more subtle.
\jc{WAVEFRONT}
